Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Remove duplicated citation to WSSSPE1 report.

Each author was invited to outline the key action from their paper as a
potential discussion point for the group; where the authors were not present,
the group facilitators outlined the actionable points from their papers. The key
actions from the six papers included recommendations for improving practice in
sustainable software engineering~\cite{wssspe2_rosada_de_souza, wssspe2_downs};
development of \emph{Software and Infrastructure as a Service} as a mechanism for
fostering sustainable science communities~\cite{wssspe2_patra}; developer
incentives for code contributions to open source projects~\cite{wssspe2_pierce};
establishment of a set of software engineering principles based on scalability,
reproducibility, and energy efficiency~\cite{wssspe2_shi}; and applying software
architectures as a mechanism for architectural-level reasoning about
sustainability~\cite{wssspe2_venters}. The group took the position of viewing
sustainability from the perspective of addressing the challenges related to the
development, deployment, and maintenance of reusable
software~\cite{katzJORS2014}.

>>>>

Each author was invited to outline the key action from their paper as a
potential discussion point for the group; where the authors were not present,
the group facilitators outlined the actionable points from their papers. The key
actions from the six papers included recommendations for improving practice in
sustainable software engineering~\cite{wssspe2_rosada_de_souza, wssspe2_downs};
development of \emph{Software and Infrastructure as a Service} as a mechanism for
fostering sustainable science communities~\cite{wssspe2_patra}; developer
incentives for code contributions to open source projects~\cite{wssspe2_pierce};
establishment of a set of software engineering principles based on scalability,
reproducibility, and energy efficiency~\cite{wssspe2_shi}; and applying software
architectures as a mechanism for architectural-level reasoning about
sustainability~\cite{wssspe2_venters}. The group took the position of viewing
sustainability from the perspective of addressing the challenges related to the
development, deployment, and maintenance of reusable
software~\cite{WSSSPE1}.
